Appendix 4: example of index standardization of fishery-independent survey data with inlabru

### 2021-12-10 doc/appendix-pcod-inlabru.Rmd
number appendices and cite them in paper

---
title: "Annotated example of index standardization with inlabru"
output:
  pdf_document:
    highlight: tango
---

@@

```{r}
sdmtmb_fit <- sdmTMB(present ~ -1 + as.factor(year),
  data = pcod,
  time = "year", spde = mesh,
  family = binomial(link = "logit"),
  spatiotemporal = "off",
  priors = sdmTMBpriors(
    matern_st = pc_matern(
      range_gt = 10, range_prob = 0.05,
      sigma_lt = 2, sigma_prob = 0.05
    )
  )
)
sdmtmb_coefs <- tidy(sdmtmb_fit, effects = "fixed")
```

>>>>

---
title: "Appendix 4: example of index standardization of fishery-independent survey data with inlabru"
output:
  pdf_document:
    highlight: tango
---

@@

```{r}
sdmtmb_fit <- sdmTMB(present ~ -1 + as.factor(year),
  data = pcod,
  time = "year", mesh = mesh,
  family = binomial(link = "logit"),
  spatiotemporal = "off",
  priors = sdmTMBpriors(
    matern_st = pc_matern(
      range_gt = 10, range_prob = 0.05,
      sigma_lt = 2, sigma_prob = 0.05
    )
  )
)
sdmtmb_coefs <- tidy(sdmtmb_fit, effects = "fixed")
```
